\documentclass[a4paper,12pt]{letter}

\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{lmargin=1in}
\geometry{rmargin=1in}


\geometry{tmargin=0.5in}
\geometry{bmargin=1cm}

% Some of the article customisations are relevant for this class

\name{Bodey} % To be used for the return address on the envelope
\signature{Bodey Baker} % Goes after the closing (ie at the end of the letter, with space for a signature)
%\address{Bodey Baker \\ Seoul, Korea}
% Alternatively, these may be set on an individual basis within each letter environment.

%\makelabels % this command prints envelope labels on the final page of the document

\begin{document}
\begin{letter}{SpaceX \\ RE: Software Engineer}

\opening{Dear Hiring Manager,} %\opening{Dear Christy Xia,} % eg Hello.

%SOFTWARE ENGINEER
% 
%RESPONSIBILITIES
%
%Design and Develop rich user-focused applications that allow us to track every step in the assembly of our Falcon Rockets and Dragon Spacecraft.
%Develop mobile web applications that allow our engineers to unchain themselves from their desktops and perform their functions directly on our 550,000 sq ft production facility.
%Work with engineering and production staff to understand how they perform the functions of their job; use this knowledge to create applications that make their lives easier.
%Be creative. Take a traditionally mundane application, such as an Inventory Tracking System, into the 21st century -- add 3D modeling, touch interfaces, photo capture, drag-and-drop functionality, geo-tagging, etc.
%BASIC QUALIFICATIONS:
%
%Bachelor’s Degree in Computer Science or raw knowledge sharpened over years of self-pursuit
%At least 2 years of experience designing and coding web based applications
%PREFERRED SKILLS AND EXPERIENCE
%
%Strong coding skills in one or more language (C#, Ruby, Java, Python, Django, PHP, C++, Obj-C, etc.)
%Prior experience with the Microsoft web stack -- C#, ASP.Net, SQL and Windows Server or a strong willingness to learn
%Experience with iOS or GWT mobile applications development
%Experience with HTML5, CSS3, AJAX/JavaScript
%Excellent problem solving skills and the ability to get things done in a fast paced startup culture
%Strong team skills with the ability to work closely with and mentor other engineers
%Passion for advancing space technologies and exploration
%Must have excellent oral and written communication skills and the ability to help define and document requirements for various projects


As a successful, experienced Software Engineer, I am confident that I will excel as a Software Engineer at SpaceX. My drive to learn and be challenged as well as my experience getting tasks done quickly in an avionics startup will allow me to make numerous contributions with SpaceX.

I believe these qualities make me a great addition to your team:

\begin{itemize}
\item Experience designing and coding software that sill used by technicians in the field.
\item Experience working 
\begin{itemize}
\item Started writing a web based platform for learning \\ Korean this year while teaching English in Korea.
\end{itemize}
\item Was a key member in a small startup where I had to multitask, quickly get up to speed on new technologies and effectively communicate with co-workers and customers.
\item Participated in decisions on frameworks, future development and best practices.
\item Researched, recommended and deployed productivity tools that were efficient, \\ liked and used.
\item Worked with military clients where security was paramount.
\item Wrote and designed software to meet expected feature specifications and \\ communicated these to fellow co-workers.
\item Spent time writing software for embedded systems where you must determine if an issue is in hardware, the operating system, the network or software.
\item Automated and streamlined repetitive parts of deployment and testing for portable servers.
\item Designed and written parallel and multi-threaded software / architectures.
\item Maintained and and analysed legacy software for performance and best practices.
\end{itemize}

I am most interested in learning more about the Software Engineering role at SpaceX. If you have any questions, please feel free to contact me at bodey.baker@gmail.com or +82-10-6589-1006.

\closing{Sincerely} % eg Regards,

%\cc{} % people this letter is cc-ed to
%\encl{} % list of anything enclosed
%\ps{} % any post scriptums. ``PS'' labels must be put in manually

\end{letter}
\end{document}