\documentclass[10pt, a4paper]{report}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{lmargin=1cm}
\geometry{tmargin=1cm}

%\DeclareFontFamily{LY1}{HoeflerText}{}\DeclareFontShape{LY1}{HoeflerText}{m}{n}%
%{ < -> LY1--HoeflerText-Regular }{}
%\DeclareFontShape{LY1}{HoeflerText}{m}{it}{ < -> LY1--HoeflerText-Italic }{}
%\DeclareFontShape{LY1}{HoeflerText}{m}{sl}{ < -> LY1--HoeflerText-Bold }{}
%\DeclareFontShape{LY1}{HoeflerText}{b}{n}{ < -> LY1--HoeflerText-Bold }{}\DeclareFontShape{LY1}{HoeflerText}{b}{it}%
%{ < -> LY1--HoeflerText-BoldItalic }{}
%
%\usepackage[LY1]{fontenc}
%\renewcommand{\rmdefault}{HoeflerText}
%\renewcommand{\rmdefault}{Frutiger}
%\renewcommand{\rmdefault}{GillSans}
%\renewcommand{\rmdefault}{SegoeUI}

\title{Brief Article}
\author{The Author}
%\date{}                                           % Activate to display a given date or no date

\parindent 0pt
\parskip 5pt
\pagestyle{plain}

\usepackage{CJK}
\usepackage{mdwlist}
\usepackage{graphicx}
\usepackage{flafter}  % Don't place floats before their definition
\usepackage{amsmath,amssymb}  % Better maths support & more symbols
\usepackage[utf8]{inputenc} % Any characters can be typed directly from the keyboard, eg éçñ
%\usepackage{geometry} % to change the page dimensions



%empty
\newcommand{\teaching}[1]{}
\newcommand{\engineering}[1]{}
\newcommand{\verbose}[1]{}

%teaching resume (needs to be 2 pages)
%\renewcommand{\teaching}[1]{#1}
%\renewcommand{\engineering}[1]{}
%\renewcommand{\verbose}[1]{}

%Engineering CV
\renewcommand{\teaching}[1]{#1}
\renewcommand{\engineering}[1]{#1}
\renewcommand{\verbose}[1]{#1}

\newcommand{\wh}[5]{\subsubsection*{#2, #3} {\em #1} \\ \parbox[t]{14cm}{#5} }

%\newcommand{\sk}[3]{\begin{basedescript}{\desclabelstyle{\pushlabel}\desclabelwidth{10em}}
%\item[#1] #2 \end{basedescript}#3}
\newcommand{\sk}[3]{\subsubsection*{#1} {#2}{#3}}

\newcommand{\pa}[3]{\subsubsection*{#1}\begin{tabular}{lr}\parbox{22em}{#2}&\parbox{25em}{#3}\end{tabular}}


\title{Resume\\~\\of}
\author{Bodey Baker}% \\(?????????)\\ \\}


\begin{document}
%\begin{titlepage} \maketitle \end{titlepage}
\pagestyle{empty}




\begin{minipage}[t]{14.5cm}
{\LARGE Bodey Baker} \\
5th October 1984
\end{minipage} 
\hfill
\begin{minipage}[t]{12em}
\begin{flushright}
bodeybaker@gmail.com\\
0420901219
\end{flushright}
\end{minipage}



\begin{minipage}[t]{14.5cm}
%{\tiny ~\\}
\section*{Experience}
\wh{May 2008 - February 2009}
{Assistant English Teacher}
{W5 Staff Services}
{Hanaguruma bldg. Kitakan 3F\\
5-4-14 Meieki, Nakamura-ku\\
Nagoya-shi, Aichi, Japan}
{I taught english to primary and junior high school students. My duties included planning lessons, teaching and generally encouraging and communicating with the students.}

\engineering{
\wh{January 2008 - March 2008}
{Graduate Software Engineer}
{JRB Engineering}
{24 Drummond Pl. \\ West Perth WA 6005\\ Australia}
{ I wrote programs to visualise the out put of log files using Visual Studio, including the coding of DLL's. Other duties were the modelling of parts for a road rail vehicle using Autodesk Inventor.}}

\wh{July 2007 - November 2007}
{Tutor}
{The University of Western Australia}
{35 Stirling Hwy.\\ Crawley WA 6009\\ Australia}
{I tutored the units ``Modelling and Computing Analysis for Engineers" and ``Mechatronics Systems" at UWA. Work consisted of teaching and marking.}

\wh{March 2007 - December 2007}
{Research Assistant}
{CET at The University of Western Australia}
{35 Stirling Hwy.\\ Crawley WA 6009\\ Australia}
{I continued the work from my iVEC internship on analysing the variation of roughness features with direction across a rock surface, eventuating in a paper.}

\engineering{\wh{December 2006 - March 2007}
{iVEC Intern}
{University of  Western Australia}
{35 Stirling Hwy.\\ Crawley WA 6009\\ Australia}
{I completed a summer research constructing an algorithm to analyse the properties of a rock surface from 3D geometric data. While working on this project I gained practical skills in visualisation, super computing and algorithm design.}

\wh{2004 - 2006}
{Clerk}
{Mothers Foods}
{Nedlands WA\\ Australia}
{I worked as a clerk within a pressured time constrained environment with responsibilities including closing the store and handling money.}}

\section*{Education}
\subsubsection*{{\em 2006:} Computer Science Honours (2A), The University of Western Australia}
\subsubsection*{{\em 2011:} Bachelor of Computer Science and Engineering, UWA}

%	\item[Institution] The 
%	\item[Thesis] Strategy specification for teamwork in robot soccer 
%	\item[GPA (WAM)] 6.00 (74.13)
%\end{basedescript}
%%Must write about the thesis here
%\begin{basedescript}{\desclabelstyle{\pushlabel}\desclabelwidth{5em}}
%\item[Units:] \engineering{~}
%
%% \begin{description*}{\desclabelstyle{\pushlabel}\desclabelwidth{5em}}
%\begin{tabular}[h]{lr}
%{\bf Computer Vision} & High Distinction\\
%{\bf Scientific Communication} & High Distinction\\
%{\bf Visualisation} & High Distinction\\
%\end{tabular}
%\end{basedescript}

%\item[Bachelor of Computer Science and Engineering] ~
%	\begin{basedescript}{\desclabelstyle{\pushlabel}\desclabelwidth{13em}}
%	\item[Began] 2003
%	\item[Time Left] Two Semesters
%	%GPA  	\\4.152 \\
%	%WAM 	58.212
%	\item[Institution] The University of Western Australia
%	\item[Majors] Computer Science and Mechatronics
%	\end{basedescript}
%	\engineering{
%	\begin{basedescript}{\desclabelstyle{\pushlabel}\desclabelwidth{5em}}
%	\item[Units:] 
%
%% \begin{description*}{\desclabelstyle{\pushlabel}\desclabelwidth{5em}}
%\begin{tabular}[h]{lr}
%{\bf Algorithms for AI} & Distinction\\
%{\bf Embedded Systems} & Distinction\\
%{\bf Algorithms} & Distinction\\
%{\bf Robotics and Automation} & Credit\\
%{\bf Real-time Distributed Computer Systems} & Credit\\
%{\bf Concurrent Programming} & Credit\\
%{\bf Computer Architecture} & Credit\\
%{\bf Operation Systems} & Credit\\
%{\bf Professional Computing} & Credit\\
%{\bf Mechatronics Systems} & Credit\\
%{\bf Control and Mechatronics} & Credit\\
%{\bf Manufacturing} & Credit\\
%{\bf Software Eng. Design} & Credit\\
%{\bf Engineering Dynamics} & Credit\\
%% {\bf Engineering Design} & Pass
%%{\bf Intro Elec. Eng.} & Credit\\
%%{\bf Intro Mech. Eng.} & Credit\\
%%{\bf Software Engineering 104} & Credit\\
%% {\bf Computer Engineering} & Pass
%% {\bf Intro. Prof. Eng.} & Pass
%%{\bf Object Oriented Programming} & Credit \\
%% {\bf Data Structures \& Algorithms} & Pass
%% {\bf foundations of IT} & Pass
%% {\bf Java Programming} & Pass
%% {\bf Mathematics 132} & Pass
%% {\bf Mathematics 101} & Pass
%% {\bf Mathematics 101} & Pass
%%{\bf Foundations of Computer Science} & Distinction\\
%% {\bf Physics 100} & Pass
%\end{tabular}
%	\end{basedescript}
%	}
%
%\item[Secondary Education] ~
%	\begin{basedescript}{\desclabelstyle{\pushlabel}\desclabelwidth{13em}}
%	\item[1999-2001] Manjimup Senior High School
%	\item[TER] 95.55 percentile
%	\item[TEE subjects] Calculus, Applicable Mathematics, Physics, Chemistry, \\ Geography, English
%	\end{basedescript}
%\end{description}

\section*{Scholarships and Prizes}
\subsubsection*{{\em 2007:} Top of the Computer Science honours unit ``Scientific Communication"}
\subsubsection*{{\em 2006:} Commonwealth Accommodation Scholarship}
\subsubsection*{{\em 2001:} Institute of Engineers award for attaining a TEE score above 75\% in:\\
		Chemistry, Physics, Calculus and Applicable Mathematics.}
\subsubsection*{{\em 2000:} Australian Mathematics Competition High Distinction}
\subsubsection*{{\em 1996:} Citizenship Award}

\section*{Interests}
Soccer, Martial Arts, Rock Climbing, Acrobatics, Capoeira, Open Source Software, AI.

\end{minipage}
\hfill
\begin{minipage}[t]{12em}
\begin{flushright}
~\\
\section*{Skills}

\engineering{
{\bf Operating Systems} \\
Linux \\
UNIX \\
Mac OS X \\
Windows XP/7 \\
~\\

{\bf Programming}

%\subsubsection*{Frequently Used}
Java \\
C \\
Python \\

%\subsubsection*{Used Extensively}
C++ \\
MATLAB \\
PHP \\
xHTML \\
CSS
%
%\subsubsection*{Some Experience}
%Haskell \\
%Bash

~\\

{\bf Theory} \\
Algorithms \\
Artificial Intelligence \\
Multi\-Agent Systems
Computer Vision \\
Visualisation \\
Parallel Computing

~\\

%\subsection*{Familiar Hardware}
%Cray XT3 \\
%AIBO ERS-7\\

{\bf CAD Software} \\
Autodesk Inventor \\
SolidWorks \\

~\\

{\bf Visualisation Software} \\
Amira \\
Dristi \\

~\\

{\bf Office Software} \\
MS Word \\
\LaTeX \\

~\\

{\bf Engineering} \\
Robotics \\
Embedded Systems \\

~\\

%\subsection*{Mathematics}
%Linear Algebra \\
%Statistics \\
%Control Theory \\

{\bf Modelling} \\
Dynamic Systems \\
Static Systems \\
Electrical Circuits \\
Vibration \\
}

\end{flushright}
\end{minipage} 

\newpage


\section*{Publications}
B. Baker, K. Gessner, E.J. Holden, and A. Squelch,  \emph{Automatic detection of anisotropic features on
rock surfaces}, Geosphere, Geological Society of America, (April 2008), 4(2):418-428\\
\\
B. Baker, M. Reynolds and W. Liu, \emph{Strategy specification for
  teamwork in robot soccer}, PCAR '06: Proceedings of the 2006 international
  symposium on Practical cognitive agents and robots (New York, NY, USA), ACM
  Press, 2006, pp.~129--140.\\
  \\
B. Baker, K. Gessner, E.J. Holden, and A. Squelch, \emph{Automatic analysis and 
visualisation of rock surface roughness,} Deformation in the desert (Alice Sprints, Northern 
Territory, Australia), Tectonics \& Structural Geology, Geological Society of Australia, July 
2007

\section*{Professional affiliations}
\subsubsection{UWA Association of Mechatronics Engineers}
President 2007, Social Engineer 2006
\subsubsection{UWA Computer Science Students Club}
Vice-President 2006, Ordinary Committee Member 2005

\end{document}